---
title: "Conceptual Questions"
format: html
toc: TRUE
editor_options: 
  chunk_output_type: inline
---

# Conceptual Questions

-   If your working directory is myfolder/homework/, what relative path would you specify to get the file located at myfolder/mydata.csv?

> readcsv(MyData.csv) will retrieve MyData.csv so long as anyone running this program will just need the file in their working directory.

-   What are the major benefits of using R projects?

> R projects establish a working directory, that can be shared, and provide a way to organize the various files and documents that are used to complete work.

-   What is git and what is github?

> Git is a version control software. It can track changes made to a document, or code, and allow authors to retrieve previous versions.

> Github is an online hosting service that stores git versions in a central online location so they can be easily shared.

-   What are the two main differences betwen a tibble and a data.frame?

> Tibbles are printed in such a way that they do not print the entire dataset - only what will fit on the screen.

> Tibbles also show the column formats when they print.

-   Rewrite the following nested function call using BaseR's chaining operator:

```{r}
#Original nested code indented for clarity
arrange(
  filter(
    select(
        as_tibble(iris), starts_with("Petal"), Species
          ), 
        Petal.Length < 1.55
        ), 
  Species
)
```

```{r}
#New code using |> pipe
library(dplyr)
iris_tibble2 <- as.tibble( iris |>
                          select(starts_with("Petal"), Species) |>
                          filter(Petal.Length < 1.55) |>
                          arrange(Species)
                          )

iris_tibble2
```
